---
title: "SubdirectoriesForLargeBatchRawData"
output: html_document
date: "2024-12-10"
---


# README

The objective of this workflow is to reorganize the folder structure where raw bat acoustic files are stored that were collected in the field and stored on the research P: drive. For batches of data greater than approximately 5000 files, I will move the files into new folders as batches of approximately 5000 files so that these will be more manageable in downstream analyses. 


### Set up work space and directories 
```{r}

library(data.table)
library(tidyverse)
library(beepr)
library(lubridate)
library(purrr)
library(janitor)
library(renv)
library(stringr)
library(beepr)


getwd()
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/BatLab Norway/GitHubLink/CoastalMonitoring/CoastalMonitoring"

## Setup output directory 
#dir.create("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/BatLab Norway/GitHubLink/CoastalMonitoring/Outputs")

output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/BatLab Norway/GitHubLink/CoastalMonitoring/Outputs"

file.name <- "SubdirectoriesForLargeBatchRawData"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today

#"C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/BatLab Norway/GitHubLink/CoastalMonitoring/Outputs/SubdirectoriesForLargeBatchRawData_2024-12-10"

```



```{r}
## Try fixing metadata in id.csv for processed acoustic data


#### CM-11 ####

## 09.08.2024
id <- read_csv("P:/SW_CoastalMonitoring/Data_collection_2024/CM-11/WAV/KPRO_V1_09.08.2024/id.csv")
id1 <- id

head(id1$OUTDIR)
#  "P:\\SW_CoastalMonitoring\\Data_collection_2024\\CM-11\\WAV\\KPR_V1_09.08.20
id1$OUTDIR <- gsub("KPR_V1", "KPRO_V1",id1$OUTDIR)

head(id1$OUTDIR)
# "P:\\SW_CoastalMonitoring\\Data_collection_2024\\CM-11\\WAV\\KPRO_V1_09.08.2024"

# write.csv(id1, "P:/SW_CoastalMonitoring/Data_collection_2024/CM-11/WAV/KPRO_V1_09.08.2024/id.csv")

## 31.08.2024
id <- read_csv("P:/SW_CoastalMonitoring/Data_collection_2024/CM-11/WAV/KPRO_V1_31.08.2024/id0.csv")
id1 <- id

head(id1$OUTDIR)
#  "P:\\SW_CoastalMonitoring\\Data_collection_2024\\CM-11\\WAV\\KPRO_V1_31.08.2024"
## This looks good- not sure why there was a id0 here 
## Will make a copy of a id.csv

# write.csv(id1, "P:\\SW_CoastalMonitoring\\Data_collection_2024\\CM-11\\WAV\\KPRO_V1_31.08.2024/id.csv")


#### CM-22 ####
## OBS! I forgot to use the  "row.names = FALSE" command when writing csvs for this batch and now there is an annoying index column in the original id0.csv
id <- read_csv("P:/SW_CoastalMonitoring/Data_collection_2024/CM-22/WAV/KPRO_V1/id.csv")


# Save a copy of the original csv file
# write.csv(id,"P:/SW_CoastalMonitoring/Data_collection_2024/CM-22/WAV/KPRO_V1/id0.csv", row.names = FALSE)
id1 <- id

head(id1$OUTDIR)
#  "D:\\CM-22\\WAV\\KPRO_V1"

## Correct the output directory
id1$OUTDIR <- "P:\\SW_CoastalMonitoring\\Data_collection_2024\\CM-22\\WAV\\KPRO_V1"

head(id1$OUTDIR)
# "P:\\SW_CoastalMonitoring\\Data_collection_2024\\CM-22\\WAV\\KPRO_V1"

# Create new id.csv with correct OUTDIR
#write.csv(id1, "P:/SW_CoastalMonitoring/Data_collection_2024/CM-22/WAV/KPRO_V1/id.csv", row.names = FALSE)


#### CM-28 ####
id <- read_csv("P:/SW_CoastalMonitoring/Data_collection_2024/CM-28/WAV/KPRO_V1/id01.csv")
# Save a copy of the original csv file
# write.csv(id,"P:/SW_CoastalMonitoring/Data_collection_2024/CM-28/WAV/KPRO_V1/id0.csv", row.names = FALSE)
id1 <- id

head(id1$OUTDIR)
#  "D:\\CM-28\\WAV\\KPRO_V1" 

## Correct the output directory
id1$OUTDIR <- "P:\\SW_CoastalMonitoring\\Data_collection_2024\\CM-28\\WAV\\KPRO_V1"

head(id1$OUTDIR)
# "P:\\SW_CoastalMonitoring\\Data_collection_2024\\CM-28\\WAV\\KPRO_V1"

# Create new id.csv with correct OUTDIR
# write.csv(id1, "P:/SW_CoastalMonitoring/Data_collection_2024/CM-28/WAV/KPRO_V1/id.csv", row.names = FALSE)

```




