---
title: "SubdirectoriesForLargeBatchRawData"
output: html_document
date: "2024-12-10"
---


# README

The objective of this workflow is to reorganize the folder structure where raw bat acoustic files are stored that were collected in the field and stored on the research P: drive. For batches of data greater than approximately 5000 files, I will move the files into new folders as batches of approximately 5000 files so that these will be more manageable in downstream analyses. 


### Set up work space and directories 
```{r}

library(data.table)
library(tidyverse)
library(beepr)
library(lubridate)
library(purrr)
library(janitor)
library(renv)
library(stringr)
library(beepr)


getwd()
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/BatLab Norway/GitHubLink/CoastalMonitoring/CoastalMonitoring"

## Setup output directory 
#dir.create("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/BatLab Norway/GitHubLink/CoastalMonitoring/Outputs")

output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/BatLab Norway/GitHubLink/CoastalMonitoring/Outputs"

file.name <- "SubdirectoriesForLargeBatchRawData"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today

#"C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/BatLab Norway/GitHubLink/CoastalMonitoring/Outputs/SubdirectoriesForLargeBatchRawData_2024-12-10"

```

```{r}

```




